Paper Figure Generation

### 2023-08-17 R/PaperFigureGeneration.rmd
General figure updates
Moved some plots around. Added 8h C>T cut site correlation plots.

```{r read_figure_7_data}
set.seed(8785)
NHF1PairedCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
NHF1ShuffledCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
for (i in seq_along(NHF1PairedCutSiteDistances)) {
  NHF1PairedCutSiteDistances[[i]] = list(CC_to_TT = NULL, C_to_T = NULL, non_C_to_T = NULL)
  NHF1PairedCutSiteDistances[[i]]$CC_to_TT = fread(generateFilePath(
    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
    repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "CC>TT"
  ))
  NHF1ShuffledCutSiteDistances[[i]] = getShufflePairedCutSiteDistances(NHF1PairedCutSiteDistances[[i]]$CC_to_TT)

  NHF1PairedCutSiteDistances[[i]]$C_to_T = fread(generateFilePath(
    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
    repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "C>T"
  ))

  NHF1PairedCutSiteDistances[[i]]$non_C_to_T = fread(generateFilePath(
    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
    repitition = "all_reps", filtering = "TGG_filtered",
    omittedMismatches = "C>T"
  ))
}

@@

```{r figure_7A, fig.width = 6, fig.height = 5}
print(paste0("Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$CC_to_TT)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, READ_LENGTH,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered",
                           xlim = c(12, 26), ylim = c(18.5, 32.5), xAxisBreaks = seq(13,25,3))
```
```{r figure_7B, fig.width = 6, fig.height = 5}
print(paste0("Read Length SLope: ", getReadLengthSlope(NHF1ShuffledCutSiteDistances$`1h`)))
plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, READ_LENGTH,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered Shuffled",
                           xlim = c(6,30), ylim = c(13,37))
```
```{r figure_7C, fig.width = 6, fig.height = 5}
print(paste0("Read length slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$non_C_to_T)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, READ_LENGTH,
                           title = "NHF1 1h Non-C>T All Reps TGG-filtered",
                           xlim = c(0,31), ylim = c(15,31))
```
```{r figure_7D, fig.width = 6, fig.height = 5}
print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered",
                           xlim = c(12,26), ylim = c(0,14.5),
                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
```
```{r figure_7E, fig.width = 6, fig.height = 5}
print(paste0("Coupling: ", getCouplingRate(NHF1ShuffledCutSiteDistances$`1h`)*-100, '%'))
plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered Shuffled",
                           xlim = c(12,26), ylim = c(0,14.5),
                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
```
```{r figure_7F, fig.width = 6, fig.height = 5}
print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$non_C_to_T)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h Non-C>T All Reps TGG-filtered",
                           xlim = c(0,31), ylim = c(0,31))
```

@@

```{r read_figure_S13_data}
NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered = fread(generateFilePath(
  NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
  repitition = "all_reps", filtering = "TGG_filtered",
  omittedMismatches = "C>T", additionalInformation = "atypical_position_filtering"
))
```

```{r figure_S13, fig.width = 6, fig.height = 5}
print(paste0("1h non-C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, READ_LENGTH,
                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("1h non-C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
```

```{r figure_S14, fig.width = 6, fig.height = 5}
print(paste0("1h C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$C_to_T)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, READ_LENGTH,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("1h C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$C_to_T)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))

print(paste0("8h CC>TT Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, READ_LENGTH,
                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("8h CC>TT Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
```

```{r read_figure_S14_data}
yeastPairedCutSiteDistances = list(`20min` = NULL)
yeastPairedCutSiteDistances$`20min` = list(CC_to_TT = NULL, non_C_to_T = NULL)
yeastPairedCutSiteDistances$`20min`$CC_to_TT = fread(generateFilePath(
  yeastCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
  cellType = "yeast", lesion = "CPD", timepoint = "20min",
  repitition = "all_reps", filtering = "TGG_filtered",
  includedMismatches = "CC>TT"
))

>>>>

```{r read_figure_7_data}
set.seed(8785)
NHF1PairedCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
NHF1ShuffledCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
for (i in seq_along(NHF1PairedCutSiteDistances)) {
  NHF1PairedCutSiteDistances[[i]] = list(CC_to_TT = NULL, C_to_T = NULL, Non_C_to_T_Position_Filtered = NULL)
  NHF1PairedCutSiteDistances[[i]]$CC_to_TT = fread(generateFilePath(
    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
    repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "CC>TT"
  ))
  NHF1ShuffledCutSiteDistances[[i]] = getShufflePairedCutSiteDistances(NHF1PairedCutSiteDistances[[i]]$CC_to_TT)

  NHF1PairedCutSiteDistances[[i]]$C_to_T = fread(generateFilePath(
    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
    repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "C>T"
  ))
}

NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered = fread(generateFilePath(
  NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
  repitition = "all_reps", filtering = "TGG_filtered",
  omittedMismatches = "C>T", additionalInformation = "atypical_position_filtering"
))

@@

```{r figure_7A, fig.width = 6, fig.height = 5}
print(paste0("Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$CC_to_TT)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, READ_LENGTH,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered",
                           xlim = c(12, 26), ylim = c(18.5, 32.5), xAxisBreaks = seq(13,25,3))
```
```{r figure_7B, fig.width = 6, fig.height = 5}
print(paste0("Read Length SLope: ", getReadLengthSlope(NHF1ShuffledCutSiteDistances$`1h`)))
plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, READ_LENGTH,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered Shuffled",
                           xlim = c(6,30), ylim = c(13,37))
```
```{r figure_7C, fig.width = 6, fig.height = 5}
print(paste0("Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, READ_LENGTH,
                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
```
```{r figure_7D, fig.width = 6, fig.height = 5}
print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered",
                           xlim = c(12,26), ylim = c(0,14.5),
                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
```
```{r figure_7E, fig.width = 6, fig.height = 5}
print(paste0("Coupling: ", getCouplingRate(NHF1ShuffledCutSiteDistances$`1h`)*-100, '%'))
plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered Shuffled",
                           xlim = c(12,26), ylim = c(0,14.5),
                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
```
```{r figure_7F, fig.width = 6, fig.height = 5}
print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
```

@@

```{r figure_S13, fig.width = 6, fig.height = 5}
print(paste0("8h CC>TT Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, READ_LENGTH,
                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("8h CC>TT Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
```

```{r figure_S14, fig.width = 6, fig.height = 5}
print(paste0("1h C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$C_to_T)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, READ_LENGTH,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("1h C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$C_to_T)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
print(paste0("8h C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`8h`$C_to_T)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$C_to_T, READ_LENGTH,
                           title = "NHF1 8h C>T All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3),
                           breaks = c(25000, 50000, 75000, 100000))
print(paste0("8h C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$C_to_T)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 8h C>T All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3),
                           breaks = c(25000, 50000, 75000, 100000))
```

```{r read_figure_S15_data}
yeastPairedCutSiteDistances = list(`20min` = NULL)
yeastPairedCutSiteDistances$`20min` = list(CC_to_TT = NULL, non_C_to_T = NULL)
yeastPairedCutSiteDistances$`20min`$CC_to_TT = fread(generateFilePath(
  yeastCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
  cellType = "yeast", lesion = "CPD", timepoint = "20min",
  repitition = "all_reps", filtering = "TGG_filtered",
  includedMismatches = "CC>TT"
))
